CP_MSSA

### 2025-03-17 Code/R/Research/CP_MSSA.Rmd
tsvd implementation

## 6
A <- exp(ones %o% c(-rep(0.05, 7), -0.03, -0.03) * 1:N)
w <- rep(1 / 12, 9)
phi <- ones %o% rep(0, 9)
save_file_name <- "noise_mixing"
groups_mssa <- list(1)
groups3 <- list(1)
groups_cp <- list(1)

@@

all_mv_rmse_res <- all_mv_rmse(R)
save(
  L_mssa,
  L_cp,
  L_ho,
  groups_mssa,
  groups_cp,
  groups3,
  all_mv_rmse_res,
  sd,
  file = paste0(
    "./Research/comp_results/all_",
    save_file_name,
    "_mv_comp.RData"
  )
)
print(all_mv_rmse_res)
```

>>>>

## 6
A <- 25 * exp(ones %o% c(-rep(0.05, 7), -0.03, -0.03) * 1:N)
w <- rep(1 / 12, 9)
phi <- ones %o% rep(0, 9)
save_file_name <- "noise_mixing"
groups_mssa <- list(1:2)
groups3 <- list(1)
groups_cp <- list(1:2)

@@

all_mv_rmse_res <- all_mv_rmse(R)
save(
  L_mssa,
  L_cp,
  L_ho,
  groups_mssa,
  groups_cp,
  groups3,
  all_mv_rmse_res,
  sd,
  file = paste0(
    "./Research/comp_results/all_",
    save_file_name,
    "_mv_comp.RData"
  )
)
print(all_mv_rmse_res)
 #          mssa  cp_mssa  ho_mssa
 # [1,] 1.146375 1.022726 1.016607
 # [2,] 1.146650 1.007815 1.003031
 # [3,] 1.143570 1.011152 1.003631
 # [4,] 1.130520 1.013088 1.006362
 # [5,] 1.140458 1.012965 1.006695
 # [6,] 1.138643 1.021572 1.013656
 # [7,] 1.165407 1.020490 1.011883
 # [8,] 1.375173 1.648700 1.649628
 # [9,] 1.377466 1.641191 1.643192
```
